\PaperTitle

### 2024-05-02 Final_Report/paper.tex
Added subsections to sections 3 and 4
punc error

\section{Introduction}
The ability to monitor and analyze network traffic is crucial for the efficiency and security of a network \cite{10.1145/2388576.2388608}. 
It helps to manage the overall network performance, detect and prevent malicious activities, and ensure the network is operating as intended.
The present day internet is composed of a vast variety of diverse web traffic, of which requires a more sophisticated approach to analyze and classify network traffic.\cite{10.5555/3432601.3432608}
This project investigates a variety of machine learning algorithms to see which most accurately and effectively classify web traffic based on data from a set of captured network packets.

@@

\subsection{Capturing Data}
\subsection{Data Preparation and Processing}
\subsection{Employed models}
\section{Evaluation}
This section comprehensively evaluates our models and their performance on the dataset and validating sets.
\subsection{Dataset}

\section{Discussion \& Future Work}

>>>>

\section{Introduction}
The ability to monitor and analyze network traffic is crucial for the efficiency and security of a network \cite{10.1145/2388576.2388608}. 
It helps to manage the overall network performance, detect and prevent malicious activities, and ensure the network is operating as intended.
The present day internet is composed of a vast variety of diverse web traffic, of which requires a more sophisticated approach to analyze and classify network traffic\cite{10.5555/3432601.3432608}.
This project investigates a variety of machine learning algorithms to see which most accurately and effectively classify web traffic based on data from a set of captured network packets.

@@

\subsection{Capturing Data}
\subsection{Data Preparation and Processing}
\subsection{Employed models}
\section{Evaluation}
This section comprehensively evaluates our models and their performance on the dataset and validating sets. Later, goes on to determine the model which best classified our selected websites based on network packet data.
\subsection{Dataset}
\subsection{Model Evaluation}
\subsection{Model Comparison and Evaluation Results}

\section{Discussion \& Future Work}
\subsection{Analysis of Results}
\subsection{Future Work}
